\chapter{Description of the Code} \label{appendix:code}

The codes created for this project are available in the \textbf{GitHub} repository of the project at the following address: \url{https://github.com/adrianlwn/MScProject\_OptSensors\_GP}. \\


We have developped some jupyter notebooks in  list also the \textit{Jupyter Notebooks} and python scripts used  to run and produce all the results of our project:
\begin{itemize}
	\item \texttt{parameters.py}: File containing the parameters such as the time interval times to import, the crop of the vtk files, the shape of the buildings. 
	\item \texttt{Sensor Optimisation 3rd Algorithm.ipynb}: Optimisation Full Scale with 3rd Algorithm. 
	\item \texttt{Sensor Optimisation Comparison 1-2-3.ipynb}: Optimisation Small Scale with All Algorithms. 

	\item \texttt{Sensor Optimisation TSVD.ipynb}: Optimisation Full Scale with 2nd Algorithm and TSVD GP Approximation.  
	\item \texttt{Covariance Comparison Plots.ipynb}: Computation of all the covariances approximations. 
	\item \texttt{Data Assimilation Randomized Points.ipynb}: Computation of the DA Application with optimal points and with randomized points. 
	\item \texttt{Preprocessing.ipynb}: Preprocessing Steps for the Data Analysis. 
	\item \texttt{Data Visulalisation.ipynb}: Some Early Visualisation of the Data. 

\end{itemize}


The fluidity library is stored outside of the code in the folder \texttt{../data/fluidity-master/}. \\
The VTK files are store in the folder \texttt{../data/small3DLSBU/}. \\
The temp files and various result vtk are stored in the folder \texttt{../data/data\_temp/}. \\


The main functions developed during this project, especially the optimisation algorithms, are placed in a python library named \texttt{utils} containing the following files: 

\begin{itemize}
	\item \texttt{data\_handling.py}: All the functions used to handle the vtk files, extract the subsets for the optimisation. It also allows to save the results in the VTK files for the purpose of visualisation. 
	\item \texttt{sensor\_optimisation.py}: All the functions needed to run the standard version of the Optimisation algorithms. Those functions take the covariance matrix in parameter.  
	\item \texttt{sensor\_optimisation\_tsvd.py}:  All the functions needed to run the modified versions of the Optimisation algorithms. Those functions take the data in parameter. 
	\item \texttt{config.py}: This script containts some usefull paths to find the data and save the temporary files and results. 
	\item \texttt{data\_assimilation.py}: This file contains functions to realise the data assimilation. 
\end{itemize}