\documentclass[12pt,twoside]{report}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Definitions for the title page
% Edit these to provide the correct information
% e.g. \newcommand{\reportauthor}{Timothy Kimber}

\newcommand{\reporttitle}{ Gaussian Processes for \\ Optimal Sensor Position \\[0.5cm] { \Large  MSc Project Report}}
\newcommand{\reportauthor}{Adrian \textsc{Löwenstein}}  %\\ \phantom{blank author} 
\newcommand{\supervisor}{Dr. Rossella \textsc{Arcucci} } % \\ Miguel \textsc{Molina-Solana}

\newcommand{\degreetype}{Computing (Machine Learning)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% load some definitions and default packages
\input{includes}

% load some macros
\input{notation}

\date{\today}

\begin{document}

% load title page
\input{titlepage}


% page numbering etc.
\pagenumbering{roman}
\clearpage{\pagestyle{empty}\cleardoublepage}
\setcounter{page}{1}
\pagestyle{fancy}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{abstract}
%Your abstract.
%\end{abstract}

\cleardoublepage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section*{Acknowledgments}
%Comment this out if not needed.

\clearpage{\pagestyle{empty}\cleardoublepage}

%%%%%%%%%%% TABLE OF CONTENTS 
\chapter*{Abstract}

Gaussian processes (GP) have been widely used since the 1970s in the fields of geostatistics and meteorology. Current applications are in diverse fields including sensor placement.
In this project, we propose the employment of a GP model to calculate the optimal spatial positioning of sensors to study and collect air pollution data in big cities. We will then apply the results by means of a data assimilation with the data at the optimised positions.


\chapter*{Acknowledgment}

I would like to thank \textit{Imperial College London} for the opportunity I was given to pursue my studies this prestigious university. \\

I would like to thank my supervisor Dr. Rossella Arcucci  of the \textit{Data Science Institute}, for her help and wise counselling throughout the project. \\

An finally, I would like to thank my girlfriend, and friends from Imperial College, who supported me during this project. \\



%--- table of contents
\fancyhead[RE,LO]{\sffamily {Table of Contents}}
\tableofcontents 


\clearpage{\pagestyle{empty}\cleardoublepage}
\pagenumbering{arabic}
\setcounter{page}{1}
\fancyhead[LE,RO]{\slshape \rightmark}
\fancyhead[LO,RE]{\slshape \leftmark}

\pagebreak



%%%%%%%%%%% CHAPTER: INTRODUCTION
\include{introduction}
 
%%%%%%%%%%% CHAPTER: LITERATURE REVIEW
\include{literature_review}


%% TEMP %%% CHAPTER: background
%\include{background}




%%%%%%%%%%% CHAPTER: IMPLEMENTATION
\include{implementation}

%%%%%%%%%%% CHAPTER: RESULTS
\include{results}

%% TEMP %%% CHAPTER: progress
%\include{progress}






%%%%%%%%%%% CHAPTER: CONCLUSION
\include{conclusion}



\appendix 

\include{ethical}


\include{code_read_me}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\chapter{Further Developements}


%% bibliography
\bibliographystyle{apa}
\bibliography{bibliography}

\end{document}
